Black swans in ecological time series\\ Black swans in population dynamics\\ Heavy-tailed ecological time series\\ Black swans in ecological dynamics\\ Black swan ecological dynamics\\ \ldots

### 2014-11-04 text/supp.tex
Add TODOs to supp. figures

\clearpage
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{table}{0}
\input{../analysis/stat-table}
\clearpage

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{../analysis/all-clean-ts-3.pdf}
\caption{
  All filtered times series used in our analysis. The abundances are shown on
  a log10 vertical axis. Colours indicate taxonomic classes. Open black circles
  indicate abundance values that were interpolated. Closed black circles
  indicate single abundance values that were recorded as zero but were set to
  the next lowest observed abundance.
}
    \label{fig:all-ts}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{../analysis/priors-gomp-base.pdf}
\caption{
  Probability density of the Bayesian priors for the Gompertz models. From left
  to right: (1) per capita growth rate at $\log$(abundance) = $0$: $\lambda \sim
  \mathrm{Normal}(0, 10^2)$; (2) scale parameter of t-distribution process
  noise: $\sigma \sim \mathrm{Half\mhyphen Cauchy} (0,
  2.5)$; (3) t-distribution degrees of freedom parameter: $\nu \sim
  \mathrm{Truncated\mhyphen Exponential}(0.01, \mathrm{min.} = 2)$; (4) AR1
  correlation coefficient of residuals: $\phi \sim \mathrm{Truncated \mhyphen
    Normal}(0, 1, \mathrm{min.} = -1, \mathrm{max.} = 1)$. Not shown is $b$,
  the density dependence parameter: $b \sim \mathrm{Uniform}(-1, 2)$.
}
  \label{fig:priors}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{../analysis/ts-gpdd-heavy-eg-log10-base.pdf}
\caption{
  Time series for populations with Pr($\nu < 10$) $>$ 0.5 using the base
  Gompertz population model. Panels are ordered by increasing Pr($\nu < 10$).
  Vertical axes are on a log10 scale. Colours indicate taxonomic classes. The
  labels on each panel indicate Pr($\nu < 10$) $>$ 0.5, the common name for the
  species, and the Global Population Dynamics Database ID number.
}
\label{fig:heavy-ts}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.27\textwidth]{../analysis/order-level-estimates.pdf}
\caption{
  Taxonomic-order-level posterior estimates of probability that $\nu < 10$ from
  a beta regression multilevel model accounting for the effect of time-series
  length. Estimates are at the geometric mean of time series length across all
  the data (approximately 27 time steps). Colour shading refers to the
  taxonomic classes as indicated in Fig.~\ref{fig:nu-coefs} and
  Fig.~\ref{fig:correlates} (yellow for fishes, green for insects, purple for
  birds, and red for mammals). Short vertical line segments indicate median
  posterior estimates. Long dotted vertical line throughout the figure
  indicates the median expected Pr($\nu < 10$) from the prior distribution.
}
\label{fig:order-estimates}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{../analysis/sim-gompertz.pdf}
\caption{
  Simulation testing the Gompertz estimation model when the process deviation
  draws were chosen so that $\nu$ could be estimated close to the true value
  outside the full population model (``effective $\nu$'' within a CV of 0.2 of
  specified $\nu$). The simulation was run across population $\nu$ values
  (columns) and different scenarios (colours): (1) 100 time steps and no
  observation error, (2) 50 time steps and no observation error, (3) 50 time
  steps and observation error drawn from $\mathrm{Normal} (0, 0.2^2)$ but
  ignored, and (4) 50 time steps with observation error in which the quantity
  of observation error was assumed known. Dashed horizontal lines show the true
  population values; these true values were chosen to represent approximately
  the median values as estimated from the Global Population Dynamics Database.
  Individual dots and lines
  represent a stochastic draws from the true population distribution and
  a model fitting (median and 80\% credible intervals). The panels from top to
  bottom show $1/\nu$, process noise scale parameter $\sigma$, growth rate
  parameter $\lambda$, and the density dependence parameter $b$.
}
\label{fig:sim-gompertz}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{../analysis/sim-gompertz-boxplots.pdf}
\caption{
  The distribution of median estimates from the same simulation as described in
  Fig.~\ref{fig:sim-gompertz}. The boxes show the interquartile range. The
  whiskers extend to $1.5$ times the interquartile range and outliers are shown
  as dots. Note that these distributions represent the output from only 20
  simulation iterations, so there is some level of remaining sampling noise.
  \textit{TODO wondering now if I should run these for more iterations to make
    these less noisy.}
}
\label{fig:sim-gompertz-boxplots}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{../analysis/check-sim-box.pdf}
\caption{
  The probability that $\nu < 10$ (i.e.\ the approximate probability of heavy
  tails) for the same simulation scenarios as shown in
  Fig.~\ref{fig:sim-gompertz} and Fig.~\ref{fig:sim-gompertz-boxplots}. Within
  each scenario the dots represent stochastic draws from the true population
  distributions combined with model fits.
}
\label{fig:sim-prob}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.5\textwidth]{../analysis/stan-beta-correlates}
\caption{
  Main effect posterior densities for potential correlates of heavy-tailed
  dynamics. The response variable was Pr($\nu < 10$) (approximately the
  probability of heavy tails). The beta regression model was fit on a logit
  scale with random intercepts for taxonomic class, taxonomic order, and
  species. All covariates were standardized by subtracting their mean and
  dividing by twice their standard deviation. Therefore, the coefficient values
  represent the expected effect of a change in two standard deviations of the
  raw input variable on the logit-transformed response variable.
}
    \label{fig:correlate-coefs}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.70\textwidth]{../analysis/perc-prob-increase-with-n}
\caption{
Expected percent increase in the probability of detecting heavy tails, Pr($\nu
< 10$), with an additional ten time steps of data. These values are based on
the curve shown in Fig.~\ref{fig:correlates}d, which is based on the
coefficient in Fig.~\ref{fig:correlate-coefs}. For example, we have about
a 12\% increased probability of observing heavy tails in a time series that has
60 time steps vs.\ a time series with 50 time steps.
}
\label{fig:perc-inc-p}
\end{center}
\end{figure}

>>>>

\clearpage
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{table}{0}
TODO ``Chondrichtyhes'' IS A TYPO IN THE GPDD DATA\\
TODO ADD TOTAL NUMBER OF POINTS ON RIGHT COLUMN
\input{../analysis/stat-table}
\clearpage

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{../analysis/all-clean-ts-3.pdf}
\caption{
TODO WILL SPLIT OVER PAGES BY CLASS
  All filtered times series used in our analysis. The abundances are shown on
  a log10 vertical axis. Colours indicate taxonomic classes. Open black circles
  indicate abundance values that were interpolated. Closed black circles
  indicate single abundance values that were recorded as zero but were set to
  the next lowest observed abundance.
}
    \label{fig:all-ts}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{../analysis/priors-gomp-base.pdf}
\caption{
TODO WILL ADD ALTERNATIVE $\nu$ PRIORS
  Probability density of the Bayesian priors for the Gompertz models. From left
  to right: (1) per capita growth rate at $\log$(abundance) = $0$: $\lambda \sim
  \mathrm{Normal}(0, 10^2)$; (2) scale parameter of t-distribution process
  noise: $\sigma \sim \mathrm{Half\mhyphen Cauchy} (0,
  2.5)$; (3) t-distribution degrees of freedom parameter: $\nu \sim
  \mathrm{Truncated\mhyphen Exponential}(0.01, \mathrm{min.} = 2)$; (4) AR1
  correlation coefficient of residuals: $\phi \sim \mathrm{Truncated \mhyphen
    Normal}(0, 1, \mathrm{min.} = -1, \mathrm{max.} = 1)$. Not shown is $b$,
  the density dependence parameter: $b \sim \mathrm{Uniform}(-1, 2)$.
}
  \label{fig:priors}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{../analysis/ts-gpdd-heavy-eg-log10-base.pdf}
\caption{
TODO WILL INDICATE UPS AND DOWNS AND MATCH STYLE TO FIG S1
  Time series for populations with Pr($\nu < 10$) $>$ 0.5 using the base
  Gompertz population model. Panels are ordered by increasing Pr($\nu < 10$).
  Vertical axes are on a log10 scale. Colours indicate taxonomic classes. The
  labels on each panel indicate Pr($\nu < 10$) $>$ 0.5, the common name for the
  species, and the Global Population Dynamics Database ID number.
}
\label{fig:heavy-ts}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.27\textwidth]{../analysis/order-level-estimates.pdf}
\caption{
TODO WILL COMBINE WITH COEFFICIENT POSTERIORS IN MAIN TEXT FIG 4
  Taxonomic-order-level posterior estimates of probability that $\nu < 10$ from
  a beta regression multilevel model accounting for the effect of time-series
  length. Estimates are at the geometric mean of time series length across all
  the data (approximately 27 time steps). Colour shading refers to the
  taxonomic classes as indicated in Fig.~\ref{fig:nu-coefs} and
  Fig.~\ref{fig:correlates} (yellow for fishes, green for insects, purple for
  birds, and red for mammals). Short vertical line segments indicate median
  posterior estimates. Long dotted vertical line throughout the figure
  indicates the median expected Pr($\nu < 10$) from the prior distribution.
}
\label{fig:order-estimates}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{../analysis/sim-gompertz.pdf}
\caption{
TODO WILL REMOVE ALL OR MOST OF THIS
  Simulation testing the Gompertz estimation model when the process deviation
  draws were chosen so that $\nu$ could be estimated close to the true value
  outside the full population model (``effective $\nu$'' within a CV of 0.2 of
  specified $\nu$). The simulation was run across population $\nu$ values
  (columns) and different scenarios (colours): (1) 100 time steps and no
  observation error, (2) 50 time steps and no observation error, (3) 50 time
  steps and observation error drawn from $\mathrm{Normal} (0, 0.2^2)$ but
  ignored, and (4) 50 time steps with observation error in which the quantity
  of observation error was assumed known. Dashed horizontal lines show the true
  population values; these true values were chosen to represent approximately
  the median values as estimated from the Global Population Dynamics Database.
  Individual dots and lines
  represent a stochastic draws from the true population distribution and
  a model fitting (median and 80\% credible intervals). The panels from top to
  bottom show $1/\nu$, process noise scale parameter $\sigma$, growth rate
  parameter $\lambda$, and the density dependence parameter $b$.
}
\label{fig:sim-gompertz}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{../analysis/sim-gompertz-boxplots.pdf}
\caption{
TODO WILL REMOVE ALL OR MOST OF THIS
  The distribution of median estimates from the same simulation as described in
  Fig.~\ref{fig:sim-gompertz}. The boxes show the interquartile range. The
  whiskers extend to $1.5$ times the interquartile range and outliers are shown
  as dots. Note that these distributions represent the output from only 20
  simulation iterations, so there is some level of remaining sampling noise.
}
\label{fig:sim-gompertz-boxplots}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{../analysis/check-sim-box.pdf}
\caption{
TODO WILL REMOVE ALL OR MOST OF THIS
  The probability that $\nu < 10$ (i.e.\ the approximate probability of heavy
  tails) for the same simulation scenarios as shown in
  Fig.~\ref{fig:sim-gompertz} and Fig.~\ref{fig:sim-gompertz-boxplots}. Within
  each scenario the dots represent stochastic draws from the true population
  distributions combined with model fits.
}
\label{fig:sim-prob}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.5\textwidth]{../analysis/stan-beta-correlates}
\caption{
TODO WILL MOVE TO MAIN TEXT WITH ORDER-LEVEL ESTIMATES
  Main effect posterior densities for potential correlates of heavy-tailed
  dynamics. The response variable was Pr($\nu < 10$) (approximately the
  probability of heavy tails). The beta regression model was fit on a logit
  scale with random intercepts for taxonomic class, taxonomic order, and
  species. All covariates were standardized by subtracting their mean and
  dividing by twice their standard deviation. Therefore, the coefficient values
  represent the expected effect of a change in two standard deviations of the
  raw input variable on the logit-transformed response variable.
}
    \label{fig:correlate-coefs}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.70\textwidth]{../analysis/perc-prob-increase-with-n}
\caption{
TODO WILL DELETE THIS
Expected percent increase in the probability of detecting heavy tails, Pr($\nu
< 10$), with an additional ten time steps of data. These values are based on
the curve shown in Fig.~\ref{fig:correlates}d, which is based on the
coefficient in Fig.~\ref{fig:correlate-coefs}. For example, we have about
a 12\% increased probability of observing heavy tails in a time series that has
60 time steps vs.\ a time series with 50 time steps.
}
\label{fig:perc-inc-p}
\end{center}
\end{figure}
